Object-oriented implementations of the MPDATA advection equation solver in~C++,~Python~and~Fortran

### 2013-01-10 paper/doc/paper.tex
first typo corrections to the arxiv v1

  Double precision floating-point format is used in all three implementations.
  The codes begins with the following definitions:
  \codecpp{code/cpp/listings.hpp}{listing01}{listing02}{1}
  \codepyt{code/pyt/listings.py}{listing01}{listing02}{1}
  \codefor{code/for/listings.f}{listing01}{listing02}{1}
  which provide a convenient way of switching to different precision.

@@

  Python is also definitely easiest to debug among the three languages.
  There exist great debugging tools for C++, but the debugging and development is 
    often hindered by indecipherable compiler messages flooded with lengthy type names
    stemming from employment of templates.
  OOP with Fortran is a relatively new concept, and the support for the Fortran OOP
    features among free and open source compilers, debuggers and other programming
    aids in still not mature.

@@

  Finally, the three languages differ as well with regard to availability of 
    mechanisms for leveraging shared-memory parallelisation (e.g. with multi-core processors).
  GCC supports OpenMP with Fortran and C++, as well as the C++11 built-in support for threads.
  The CPython and PyPy implementations of Python don't offer any
    built-in solution for multithreading. 
  However, there are third-party party libraries such as numexpr which can employ multiple cores from
    a single program.
  There exist object-oriented libraries for both C++ and Python to 
    transparently use graphics processing units (GPU) such as Thrust \citep{Thrust}
    and Theano \citep{Bergstra_et_al_2010}.

>>>>

  Double precision floating-point format is used in all three implementations.
  The codes begin with the following definitions:
  \codecpp{code/cpp/listings.hpp}{listing01}{listing02}{1}
  \codepyt{code/pyt/listings.py}{listing01}{listing02}{1}
  \codefor{code/for/listings.f}{listing01}{listing02}{1}
  which provide a convenient way of switching to different precision.

@@

  Python is also definitely easiest to debug among the three languages.
  There exist great debugging tools for C++, but the debugging and development is 
    often hindered by indecipherable compiler messages flooded with lengthy type names
    stemming from employment of templates.
  OOP with Fortran is a relatively new concept, and the support for the Fortran OOP
    features among free and open source compilers, debuggers and other programming
    aids is still not mature.

@@

  Finally, the three languages differ as well with regard to availability of 
    mechanisms for leveraging shared-memory parallelisation (e.g. with multi-core processors).
  GCC supports OpenMP with Fortran and C++, as well as the C++11 built-in support for threads.
  The CPython and PyPy implementations of Python do not offer any
    built-in solution for multithreading. 
  However, there are third-party party libraries such as numexpr which can employ multiple cores from
    a single program.
  There exist object-oriented libraries for both C++ and Python to 
    transparently use graphics processing units (GPU) such as Thrust \citep{Thrust}
    and Theano \citep{Bergstra_et_al_2010}.
